How do school travel planning stakeholders frame active school travel in Ontario, Canada?

### 2021-06-24 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Last Update before June 14 Meeting

```{r, include=FALSE}
library(tm)
library(readr)
library(tools)
library(DiagrammeR)
library(kableExtra)
```

@@

>>>>

```{r, include=FALSE}
library(DiagrammeR)
library(dplyr)
library(ggraph)
library(ggplot2)
library(igraph)
library(kableExtra)
library(pdftools)
library(readr)
library(reshape2)
library(stringr)
library(text2vec)
library(textdata)
library(tidyr)
library(tidytext)
library(tm) 
library(tools)
library(topicmodels)
library(widyr)
library(word2vec)
library(wordcloud)
```

@@

Academic corpus vocabulary 
```{r}
# Create new data frame with the cleaned corpus 
AcademicTextDF <- data.frame(text = sapply(academic_corpus, as.character), stringsAsFactors = FALSE)

it_train = itoken(AcademicTextDF$text, progressbar = FALSE)
academic_vocab = create_vocabulary(it_train)

# Cut out terms that have a minimum count of 5 
academic_vocab <- prune_vocabulary(academic_vocab, term_count_min = 5)
academic_vocab
```
